Semi-supervised low-rank logistic regression for high-dimensional neuroimaging data

### 2015-05-26 paper_nips/paper.tex
bertrands 1st comments on paper

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, modelling the neural correlates of mental tasks hinges
on the pertinence of the assumed neurobiological structure.
%
We therefore propose to solve the unsupervised dimensionality reduction
and supervised task classification in
an identical statistical learning problem.
%
We show that this approach yields more accurate and more interpretable
neural models of psychological tasks in a reference dataset.
%

@@

On the other hand, to investigate
the neural correlates underlying mental tasks,
the general linear model (GLM) is the dominant approach \cite{friston94}.
The contribution of
individual brain voxels is estimated
according to a design matrix of experimental tasks.
Alternatively, psychophysiological interactions (PPI)
elucidate the functional interactions between voxels as a function
of experimental tasks \cite{friston97}.
Dynamic causal modeling (DCM), in turn, quantifies directed,
task-driven influences between regions
by treating the brain as a nonlinear dynamic system with unknown
neuronal states \cite{stephan04}.
As a last example, always more neuroimaging studies model
experimental tasks by training classification algorithms on brain signals
\cite{poldrack09decoding}.
All these methods are applied to labeled task data that capture brain dynamics
during stimulus-guided behavior.
Two important conclusions can be drawn.
First, the mentioned supervised neuroimaging analyses operate
without exception in a voxel space. This ignores the fact that the BOLD
signal exhibits distributed spatial activation patterns.
Second, existing neuroimaging analyses do not acknowledge the fact that the
task-induced changes of the BOLD signal typically amount to less than 5\%
of baseline activity \cite{fox07}. They do thus not exploit the high similarity
of BOLD dynamics in the human brain at rest and during experimental tasks,
as observed using ICA \cite{smith2009}.

Both these biological properties can be conjointly exploited in a 
semi-supervised (i.e., use rest and task data)
low-rank (i.e., perform network decomposition)
approach.
%
The integration of brain-network discovery into a 
supervised classification framework should identify the most relevant
neurobiological structure for the prediction problem at hand.
%
Autoencoders suggest themselves because they can emulate
variants of most unsupervised learning algorithms,
including PCA, SPCA, and ICA \cite{hinton06}.
Autoencoders
are one-layered learning models that condense the input data to
local and global representations
by improving reconstruction from them.
%
They behave like a PCA
in case of one linear hidden layer and a squared error loss
%
\begin{wrapfigure}{r}{0.40\textwidth}
  \centering
  %\captionsetup{labelformat=nonumber}
    \includegraphics[width=0.40\textwidth]{figures/figure1.png}
  \caption {\textbf{Architecture}
  }
\end{wrapfigure}
%
\cite{baldi1989neural}.
This architecture yields a convex optimization objective
with unique global minimum.
Autoencoders behave like a SPCA if shrinkage terms are added to the
model weights in the optimization objective.
Moreover, they have the characteristics of an ICA in case of tied weights
and feeding the first-layer activation into any nonlinear convex
function \cite{le2011ica}.
These authors further demonstrated that ICA, sparse autoencoders, and 
sparse coding are mathematically equivalent
under mild conditions.
Hence, autoencoders can flexibly project the neuroimaging data
onto the main axes of variation and thus
reverse-engineer properties of the data-generating
neural processes \cite{olshausen96}.

In the present investigation,
a linear autoencoder will be fed by (unlabeled) rest data and
integrated as bottleneck
into a low-rank logistic regression fed by (labeled) task data.
Using the chain rule for gradient descent, we can then
solve the unsupervised data representation and the supervised classification
in an identical statistical learning problem.
From the perspective of dictionary learning, the first layer represents
the discovered set of basis functions
whose linear combinations are learned
by the second layer \cite{olshausen96}.
%
Neurobiologically, this allows 
delineating a low-dimensional manifold of brain network patterns and then 
distinguishing mental tasks
by their most discriminative linear combinations.
%
Theoretically, a reduction in model variance should be achieved by
resting-state autoencoders that
put probability mass on the most neurobiologically
valid models in the hypothesis set.
%
The generalization performance should consequently be improved due to 
reduced Vapnik-Chervonenkis dimensions of the trained estimator.
%
Taken together,
the important modes of variation in brain dynamics and
the neural correlates subserving mental operations
have mostly been studied in isolation.
We provide a principled computational framework to link these previously
unconnected domains of systems neuroscience.

\section{Methods}
%
\paragraph{Data.}
As the currently biggest openly-accessible reference dataset,
we chose the Human Connectome Project (HCP) resources
\cite{barch2013}.
Neuroimaging task data with labels of ongoing cognitive processes
were drawn from 500 unrelated,
healthy HCP participants.
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
The task paradigms include
1) working memory/cognitive control processing, 2)
incentive processing, 3) visual and somatosensory-motor processing,
4) language processing (semantic and phonological processing),
5) social cognition, 6) relational processing, and 7) emotional
processing. All data were acquired on the same Siemens Skyra 3T scanner.
Whole-brain EPI acquisitions were acquired with a
32 channel head coil (TR=720ms, TE=33.1ms, flip angle=52°, BW=2290Hz/Px,
in-plane FOV=$280\times180$mm, 72 slices, 2.0mm isotropic voxels).
The ``minimally preprocessed'' pipeline includes
gradient unwarping, motion correction, fieldmap-based EPI distortion
correction, brain-boundary-based registration of EPI to structural
T1-weighted scans, nonlinear (FNIRT) registration into MNI space,
and grand-mean intensity normalization. Activation maps were spatially
smoothed by a Gaussian kernel of 4mm (FWHM). A GLM was
implemented by FILM from the FSL suite with model regressors from convolution
with a “canonical” hemodynamic response function and from temporal derivatives.
HCP tasks were conceived to modulate activation
in a maximum of different brain regions and neural systems. Indeed, at
least 70\% of the participants showed consistent brain activity in
contrasts from the task battery, which certifies excellent
coverage \cite{barch2013}.
In sum, the HCP task data incorporated 8650 first-level activity maps
from 18 diverse paradigms administered to 498 participants (2 removed
due to incomplete data).
All maps were resampled to a common 60x72x60 space of
3mm isotropic voxels and gray-matter masked (at least 10\% tissue
probability).
The supservised analyses were based on labeled HCP task maps with
79,941 voxels of interest representing z-values in gray matter.

@@

where $x \in \mathbb{R}^{d}$ denotes the vector of $d=79,941$
voxel values from each
rest map, $z \in \mathbb{R}^{n}$ is the $n$ hidden dimensions (i.e.,
distributed neural activity patterns), and 
$x' \in \mathbb{R}^{d}$ is the reconstruction vector of the original activity map
from the hidden variables. Further, ${W_0}$ denotes the weight matrix that
transforms
from input space into the hidden space (encoder),
${W_1}$ is the weight matrix for back-projection from the hidden variables to the
output space (decoder).
${b_{W_0}}$ and ${b_{W_1}}$ are bias vectors.
Note that ${W_0}$ and ${W_1}$ are tied,
$W_0$ = $W_1^T$.
The optimal model parameters ${W_0}, {b_{W_0}}, {b_{W_1}}$ are found by
minimizing the imperfection of reconstruction according to squared error

@@

\begin{eqnarray}
  \begin{split}
    P(Y=i|x, V_0,V_1,b_{V_0}, b_{V_1}) &= softmax_i(V_1 (V_0 x + b_{V_0}) + b_{V_1}) \\
    &= \frac {e^{V_1_i (V_0_i x + b_{V_0}_i) + b_{V_1}_i}} {\sum_j e^{V_1_j (V_0_j x + b_{V_0}_j) + b_{V_1}_j}}            
  \end{split}
  \label{eq:lr}
\end{eqnarray}

@@

\paragraph{Optimization.}
The common objective was approximated in the neuroimaging data
by updating parameters by derivates of the 
semi-supervised low-rank logistic regression.
The required gradients are easily obtained by using the chain rule to
backpropagate error derivatives through the linear network.
As solver, we chose \textit{rmsprop} \cite{rmsprop},
a mini-batch version of rprop.
This procedure dictates an adaptive learning rate
for each model parameter by
scaled gradients from a running average.
Gradient normalization by rmsprop
is known to effectively exploit curvature information.
We opted for a small batch size of $100$, given the high degree of
redundancy in $X_{rest}$ and $X_{task}$.
The matrix parameters were initalized by Gaussian random values multiplied
by a gain of $0.004$. The bias parameters were initalized to zero.
With a slight abuse of notation, let $\theta$ denote a component of $\theta$.
The normalization factor and the update rule for $\theta$
are given by

@@

where $0 < \rho < 1$ constitutes the decay rate. $\rho$ was set to
$0.9$ to deemphasize the magnitude of the gradient.
Further, $\alpha$ is the learning rate and $\epsilon$ a global damping factor.
The hyper-parameter $\alpha$ was set to $0.00001$ by prior manual
cross-validation and $\epsilon$ was set to $10^{-6}$.
%
Note that we have also experimented with other solvers
(stochastic gradient descent, adadelta, and adagrad) but found that
rmsprop converged faster and with higher generalization performance.

@@

\bigskip

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/accuracies.png}
\end{centering}
\caption{\textbf{Generalization performance}
Depicts in-sample (apply current model on training set, \textit{left column}),
out-of-sample (current model on test set, \textit{middle column}),
and out-of-dataset (compress other dataset using the
learned decomposition for classification, \textit{right column}) accuracy.
Curves for different choices of $\lambda$ as well as for ordinary
logistic regression (\textit{yellowish})
across iterations over the HCP task data (epochs).
}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/figure_weights.jpg}
\end{centering}
\caption{\textbf{Comparing the interpretability of classification weights}
The voxel predictors corresponding to 5 (of 18) psychological tasks (\textit{rows})
from the HCP dataset \cite{barch2013}.
\textit{Left column:} ordinary logistic regression (based on same
implementation but without bottleneck layer or autoencoder),
\textit{middle column:} semi-supervised low-rank logistic regression
(latent components $n=20$, $\lambda=0.5$, $\ell_1=0.1$, $\ell_2=0.1$),
\textit{right column:} voxel-wise average of whole-brain activity
across the first-level activity maps from 498 participants
(thresholded at 0.25).
All values z-scored.
}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/support_bars.png}
\end{centering}
\caption{\textbf{Relation between support recovery and out-of-dataset performance}
\textit{Upper row:} the fit-for-purpose of the classification models
is quantified by linear correlation between the
z-scored average task image and the z-scored weights from
ordinary (\textit{red}) and present (\textit{blue colors}) logistic
regression ($\lambda=0.25, 0.50, 0.75, 1.00$).
\textit{Lower row:} ordinary logistic regression is applied to the
ARCHI dataset after projection into the latent dimensions learned from
the HCP task data.
}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.40\textwidth]{figures/figure3.png}
  \end{center}
  \caption {\textbf{
  Equilibrium between autoencoder and low-rank logistic regression}
  One learned decomposition component (out of 20) between the only-autoencoder
  (\textit{uppermost panel}) and only-logistic-regression
  (\textit{lowermost panel}) scenarios.
  The congruent structure (\textit{red, middle column})
  in the
  posterior cingulate cortex, posterior mid-cingulate cortex, and medial
  prefrontal cortex appears to be important in decompositions of the rest and
  task neuroimaging data. With increasing weight on the supervised learning,
  non-congruent structure emerges in the early (\textit{blue}) and
  lateral (\textit{red}) visual cortex
  (\textit{right column}). Matrix weights were z-scored.
  }
\end{figure}

\section{Discussion and Conclusion}
%
There is an increasing occurrence of high-dimensional problems in the
neuroimaging domain. Yet, there is also considerable uncertainty about the
most pertinent representation
of neural activation information.
This calls for new statistical learning algorithms that
behave well in large samples. Ideally, they should acknowledge
and exploit widely-accepted neuroscientific knowledge.
We here propose such an estimator that learns
dimensionality reduction
in a neurobiological and interpretable fashion.

>>>>

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.
%
Existing neuroimaging methods typically perform either discovery of unknown
neural structure or testing of neural structure associated with mental tasks.
%
However, modelling the neural correlates of mental tasks hinges
on the pertinence of the assumed neurobiological structure.
%XXX: this last statement is not cristal clear.
%
% XXX: Big gap between these two sentences. It is unclear what you call 'supervised' or 'unsupervised'.
%
We therefore propose to solve the unsupervised dimensionality reduction
and supervised task classification in
an identical statistical learning problem.
%
We show that this approach yields more accurate and more interpretable
neural models of psychological tasks in a reference dataset.
%

@@

On the other hand, to investigate
the neural correlates underlying mental tasks,
the general linear model (GLM) is the dominant approach \cite{friston94}.
The contribution of
individual brain voxels is estimated
according to a design matrix of experimental tasks.
Alternatively, psychophysiological interactions (PPI)
elucidate the functional interactions between voxels as a function
of experimental tasks \cite{friston97}.
Dynamic causal modeling (DCM), in turn, quantifies directed,
task-driven influences between regions
by treating the brain as a nonlinear dynamic system with unknown
neuronal states \cite{stephan04}.
As a last example, always more neuroimaging studies model
experimental tasks by training classification algorithms on brain signals
\cite{poldrack09decoding}.
All these methods are applied to labeled task data that capture brain dynamics
during stimulus-guided behavior.
Two important conclusions can be drawn.
First, the mentioned supervised neuroimaging analyses operate
without exception in a voxel space. 
%XXX:not exactly: the DCM is based on ROIs typically. PPI also ?

This ignores the fact that the BOLD
signal exhibits distributed spatial activation patterns.
Second, existing neuroimaging analyses do not acknowledge the fact that the
task-induced changes of the BOLD signal typically amount to less than 5\%
of baseline activity \cite{fox07}. 
%
% XXX I think that this is wrong. Moreover, it is not completely  clear how crucial this is. I think that there are better arguments to introduce the joint analysis of rest and task.
% For example, the existence of abundant RS data is an important practical reson to consider them. 'Better sample the manifold of brain states'
% 
They do thus not exploit the high similarity
of BOLD dynamics in the human brain at rest and during experimental tasks,
as observed using ICA \cite{smith2009}.

Both these biological properties can be conjointly exploited in a mixed
 (i.e., use rest and task data)
low-rank (i.e., perform network decomposition)
approach.
%
The integration of brain-network discovery into a 
supervised classification formally yields a semi-supervised learning framework that should identify the most relevant
neurobiological structure for the prediction problem at hand.
%
Autoencoders suggest themselves because they can emulate
variants of most unsupervised learning algorithms,
including PCA, SPCA, and ICA \cite{hinton06}.
Autoencoders
are one-layered learning models that condense the input data to
local and global representations
by improving reconstruction from them.
%
They behave like a PCA
in case of one linear hidden layer and a squared error loss
%
\begin{wrapfigure}{r}{0.40\textwidth}
  \centering
  %\captionsetup{labelformat=nonumber}
    \includegraphics[width=0.40\textwidth]{figures/figure1.png}
  \caption {\textbf{Architecture. XXX develop the cpation. Main msg ?}
  }
\end{wrapfigure}
%
\cite{baldi1989neural}.
This architecture yields a convex optimization objective
with unique global minimum.
Autoencoders behave like a SPCA if shrinkage terms are added to the
model weights in the optimization objective.
Moreover, they have the characteristics of an ICA in case of tied weights
and feeding the first-layer activation into any nonlinear convex
%% ICA contrasts are rarely convex ?!?
function \cite{le2011ica}.
These authors further demonstrated that ICA, sparse autoencoders, and 
sparse coding are mathematically equivalent
under mild conditions.
%
Hence, autoencoders can flexibly project the neuroimaging data
onto the main axes of variation and thus
reverse-engineer properties of the underlying
neural processes \cite{olshausen96}.

In the present investigation,
a linear autoencoder will be fed by (unlabeled) rest data and
integrated as bottleneck
into a low-rank logistic regression fed by (labeled) task data.
% Using the chain rule for gradient descent, 
We can then solve the unsupervised data representation and the
supervised classification in an identical statistical learning
problem.
%
From the perspective of dictionary learning, the first layer represents
the discovered set of basis functions
whose linear combinations are learned
by the second layer \cite{olshausen96}.
%
Neurobiologically, this allows 
delineating a low-dimensional manifold of brain network patterns and then 
distinguishing mental tasks
by their most discriminative linear combinations.
%
Theoretically, a reduction in model variance should be achieved by
resting-state autoencoders that
put probability mass on the most neurobiologically
valid models in the hypothesis set.
%
The generalization performance should consequently be improved due to 
reduced Vapnik-Chervonenkis dimensions of the trained estimator.
% I would not make direct claims on *VC* dimension, since you don't consider it explictly
%
Taken together,
the important modes of variation in brain dynamics and
the neural correlates subserving mental operations
have mostly been studied in isolation.
We provide a principled computational framework to link these previously
unconnected domains of systems neuroscience.

\section{Methods}
%
\paragraph{Data.}
As the currently biggest openly-accessible reference dataset,
we chose the Human Connectome Project (HCP) resources
\cite{barch2013}.
Neuroimaging task data with labels of ongoing cognitive processes
were drawn from 500 unrelated,
healthy HCP participants.
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants.
The task paradigms include
1) working memory/cognitive control processing, 2)
incentive processing, 3) visual and somatosensory-motor processing,
4) language processing (semantic and phonological processing),
5) social cognition, 6) relational processing, and 7) emotional
processing. All data were acquired on the same Siemens Skyra 3T scanner.
Whole-brain EPI acquisitions were acquired with a
32 channel head coil (TR=720ms, TE=33.1ms, flip angle=52°, BW=2290Hz/Px,
in-plane FOV=$280\times180$mm, 72 slices, 2.0mm isotropic voxels).
The ``minimally preprocessed'' pipeline includes
gradient unwarping, motion correction, fieldmap-based EPI distortion
correction, brain-boundary-based registration of EPI to structural
T1-weighted scans, nonlinear (FNIRT) registration into MNI space,
and grand-mean intensity normalization. Activation maps were spatially
smoothed with a Gaussian kernel of 4mm (FWHM). A GLM was
implemented by FILM from the FSL suite with model regressors from convolution
with a “canonical” hemodynamic response function and from temporal derivatives.
HCP tasks were conceived to modulate activation
in a maximum of different brain regions and neural systems. Indeed, at
least 70\% of the participants showed consistent brain activity in
contrasts from the task battery, which certifies excellent
coverage \cite{barch2013}.
%
% No, this is not what is called 'coverage'
%
In sum, the HCP task data incorporated 8650 first-level activity maps
from 18 diverse paradigms administered to 498 participants (2 removed
due to incomplete data).
All maps were resampled to a common 60x72x60 space of
3mm isotropic voxels and gray-matter masked (at least 10\% tissue
probability).
The supservised analyses were based on labeled HCP task maps with
79,941 voxels of interest representing z-values in gray matter.

@@

where $x \in \mathbb{R}^{d}$ denotes the vector of $d=79,941$
voxel values from each
rest map, $z \in \mathbb{R}^{n}$ is the $n$ hidden dimensions (i.e.,
distributed neural activity patterns), and 
$x' \in \mathbb{R}^{d}$ is the reconstruction vector of the original activity map
from the hidden variables. 
% XXX use bold letters for vectors and matrices
Further, ${W_0}$ denotes the weight matrix that
transforms
from input space into the hidden space (encoder),
${W_1}$ is the weight matrix for back-projection from the hidden variables to the
output space (decoder).
${b_{W_0}}$ and ${b_{W_1}}$ are bias vectors.
Note that ${W_0}$ and ${W_1}$ are tied,
$W_0$ = $W_1^T$.
The optimal model parameters ${W_0}, {b_{W_0}}, {b_{W_1}}$ are found by
minimizing the imperfection of reconstruction according to squared error

@@

\begin{eqnarray}
  \begin{split}
    P(Y=i|x, V_0,V_1,b_{V_0}, b_{V_1}) &= softmax_i(V_1 (V_0 x + b_{V_0}) + b_{V_1}) \\
    &= \frac {e^{V_{1i} (V_{0i} x + b_{V_{0i}}) + b_{V_{1i}}}} {\sum_j e^{V_{1j} (V_{0j} x + b_{V_{0j}}) + b_{V_{1j}}}}            
  \end{split}
  \label{eq:lr}
\end{eqnarray}

@@

\paragraph{Optimization.}
The common objective was approximated 
% XXX why 'approximated' ?
in the neuroimaging data
by updating parameters by derivates 
% XXX derivates ???
of the 
semi-supervised low-rank logistic regression.
The required gradients are easily obtained by using the chain rule to
backpropagate error derivatives through the linear network.
As solver, we chose \textit{rmsprop} \cite{rmsprop},
a mini-batch version of rprop.
This procedure dictates an adaptive learning rate
for each model parameter by
scaled gradients from a running average.
Gradient normalization by rmsprop
is known to effectively exploit curvature information.
We opted for a small batch size of $100$, given the high degree of
redundancy in $X_{rest}$ and $X_{task}$.
The matrix parameters were initalized by Gaussian random values multiplied
by a gain of $0.004$. The bias parameters were initalized to zero.
With a slight abuse of notation, let $\theta$ denote a component of $\theta$.
The normalization factor and the update rule for $\theta$
are given by

@@

where $0 < \rho < 1$ constitutes the decay rate. $\rho$ was set to
$0.9$ to deemphasize the magnitude of the gradient.
Further, $\alpha$ is the learning rate and $\epsilon$ a global damping factor.
The hyper-parameter $\alpha$ was set to $0.00001$ by prior studies and $\epsilon$ was set to $10^{-6}$.
%
Note that we have also experimented with other solvers
(stochastic gradient descent, adadelta, and adagrad) but found that
rmsprop converged faster and with higher generalization performance.

@@

\bigskip
% XXX the accuracy figure is not very nice. export is in pdf.
% XXX change the titles. remove the resolution information from the title.
% XXX larger legends. they're not readable currently
\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/accuracies.png}
\end{centering}
\caption{\textbf{Generalization performance}
Depicts in-sample (apply current model on training set, \textit{left column}),
out-of-sample (current model on test set, \textit{middle column}),
and out-of-dataset (compress other dataset using the
learned decomposition for classification, \textit{right column}) accuracy.
Curves for different choices of $\lambda$ as well as for ordinary
logistic regression (\textit{yellowish})
across iterations over the HCP task data (epochs).
XXX: Message ??
}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/figure_weights.jpg}
\end{centering}
\caption{\textbf{Comparing the interpretability of classification weights}
The voxel predictors corresponding to 5 (of 18) psychological tasks (\textit{rows})
from the HCP dataset \cite{barch2013}.
\textit{Left column:} ordinary logistic regression (based on same
implementation but without bottleneck layer or autoencoder),
\textit{middle column:} semi-supervised low-rank logistic regression
(latent components $n=20$, $\lambda=0.5$, $\ell_1=0.1$, $\ell_2=0.1$),
\textit{right column:} voxel-wise average of whole-brain activity
across the first-level activity maps from 498 participants
(thresholded at 0.25).
All values are z-scored.
% XXX: Why is the z-map sparse ?!? 
}
\end{figure}

\begin{figure}
% XXX: figure not readable
\begin{centering}
\includegraphics[width=1.00\textwidth]{figures/support_bars.png}
\end{centering}
\caption{\textbf{Relation between support recovery and out-of-dataset performance}
\textit{Upper row:} the fit-for-purpose of the classification models
is quantified by linear correlation between the
z-scored average task image and the z-scored weights from
ordinary (\textit{red}) and present (\textit{blue colors}) logistic
regression ($\lambda=0.25, 0.50, 0.75, 1.00$).
\textit{Lower row:} ordinary logistic regression is applied to the
ARCHI dataset after projection into the latent dimensions learned from
the HCP task data.
}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.40\textwidth]{figures/figure3.png}
  \end{center}
  \caption {\textbf{
  Equilibrium between autoencoder and low-rank logistic regression}
  One learned decomposition component (out of 20) between the only-autoencoder
  (\textit{uppermost panel}) and only-logistic-regression
  (\textit{lowermost panel}) scenarios.
  The congruent structure (\textit{red, middle column})
  in the
  posterior cingulate cortex, posterior mid-cingulate cortex, and medial
  prefrontal cortex appears to be important in decompositions of the rest and
  task neuroimaging data. With increasing weight on the supervised learning,
  non-congruent structure emerges in the early (\textit{blue}) and
  lateral (\textit{red}) visual cortex
  (\textit{right column}). Matrix weights were z-scored.
% XXX To me there is no clear message here. You can always interpolate between arbitrary maps... What does this bring to you ? 
 }
\end{figure}

\section{Discussion and Conclusion}
%
There is an increasing occurrence of high-dimensional problems in the
neuroimaging domain. 
%
% XXX: meaningless and useless for your work
%
Yet, there is also considerable uncertainty about the
most pertinent representation
of neural activation information.
This calls for new statistical learning algorithms that
behave well in large samples. Ideally, they should acknowledge
and exploit widely-accepted neuroscientific knowledge.
We here propose such an estimator that learns
dimensionality reduction
in a neurobiological and interpretable fashion.
% You really should emphasize the problem of accumulating data and knowledge which is much more interesting. Cite Yannick.
